Tables

### 2023-10-16 output/paper/tables.qmd
Tried pre-release of Quarto 1.4 to fix issue with cross-ref of tables but it fails to render PDF. Went back to stable release.
Modified pipelines to handle ratios as outcome or exposure correctly.
Trying to solve cross ref with gt and docx.
How the fuck do I cross ref across files?

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

- Begin each table on a new page after the list of references.
- Tables may not contain parts.
- List footnotes after the general one, one per line and indicated with a lowercase italicized letter.

# Study populations
```{r}

```

# Exposures
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.

@@

>>>>

editor_options:
  chunk_output_type: console

execute:
  echo: false
  warning: false
  error: false
  message: false
---

- Begin each table on a new page after the list of references.
- Tables may not contain parts.
- Provide the title for each table above the table and the notes below the table.
- List footnotes after the general one, one per line and indicated with a lowercase italicized letter.

# Descriptive data

## Study populations

- Basic characteristics of study participants (demographic, clinical, social), by cohort and overall.
  - Include all covariates included in primary or secondary analyses.
  - Indicate number of participants with missing data for each variable of interest.
  - Report numbers of outcome events or summary measures.

## Endocrine disruptors

- Levels of unprocessed biomarkers (chemicals), with IDs.
- Report: minimum and maximum, percentiles, and number of observations above/below the assay's LOD and LOQ.

```{r}
#| label: tbl-chem-info
#| tbl-cap: "Information about the non-persistent EDCs."

@@

## Corticosteroids

- Levels of unprocessed biomarkers (metabolites), with IDs.
- Table comparing subjects with and without measurement of steroids.

# Main results

- RQ2: group chemicals by class, and for each chemical report results with metabolites (`avg_comparisons` with estimate, SE, s-value, CI).
- RQ3: report results with outcome (`avg_comparisons` with estimate, SE, s-value, CI).

# Other analyses
